---
title: "Milestone 4/5/2019"
author: "Neil Khurana"
date: "April 5, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(readr)
```

The following contain all the meals from Harvard University Dining Services as of 11/10/2018. There was a script available on the Harvard Open Data Project website that basically scrapes all the dining data from that day to today. Harvard Open Data is a student organization on campus that tries to make data sets available to the public and they also do some analysis on their own. As a memeber of Harvard Open Data Project, not only is this project going to be for my class but I will write a data journalism article for the Open Data Project website. I am thinking of taking all the meals from last winter semester and seeing the repitition/frequency of meals within the semester. I am still not completely sure about everything else I could map out but could maybe also do a cross comparision across lunch and dinner.   

Below I have a gpplot that maps out. 

```{r plot}
huds <- read_csv("HUDS_Menu_Data.csv")



```
